Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-04-22 tex/VHzQ.tex
wee tex/VHzQ.tex, .pdf update
VHzQ updated again

@@

>>>>

     There are 17 objects that have no NIR detections. 
     2 of these (PSOJ053.9605-15.7956 and PSO J056.7168-16.4769) 
     have been observed, but are out of our queried time range. 
     10 objects have not been observed (or at least the data is not in the WSA/VSA 
     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
     and cannot be observed.

@@

       %% http://svo2.cab.inta-csic.es/svo/theory/fps/index.php?mode=browse&gname=UKIRT&gname2=WFCAM
     %% emails around 16 Aug 2018, Carlos Rodrigo
     %%     (-2.5)*(log10( ZP_in_Jy / 3631.0)) 
